---
title: "Linear & Logistic Regression - Answers"
author: "Samantha-Jo Caetano"
date: "May 13, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In your breakout groups work through the following R code:

```{r}
library(tidyverse)
```


# Loading in Data


The `dpylr` package has some data about Star Wars characters. Let's assume it is a representative sample of all characters seen in Episodes 1 to 9.


```{r, message=FALSE}

starwars<-starwars

glimpse(starwars)

head(starwars)

```


### Task 1: Create a Simple Linear Model to predict mass

Use the `svyglm()` function in the `survey` library to run a linear regression estimation of mass given height. Assume it was a Simple Random Sample and use the finite population correction with $N=200$.

```{r}
#install.packages("survey")
library(survey)

## Using the Survey Library
n=87
N=200



```

What is the standard error of the intercept?

a. -13.81
b. 17.36
c. 0.64
d. 0.06


### Task 2: Create a Linear Model to predict mass

Use the `lm()` function in the `survey` library to run a linear regression estimation of mass given height.

```{r}
#install.packages("survey")
library(survey)

## Using the Survey Library


```

What is the different between the output here and the outcome in Task 1? What is similar?



What happens if you change the $N$ in Task 1? Try setting $N=87, 200, 1000, 10000$


### Task 3: Create a Linear Model to predict mass

Run a linear regression estimation of mass given height and sex.

```{r}
## Using the Survey Library
n=87
N=200
fpc.srs = rep(N, n)

starwars.design <- svydesign(id=~1, data=starwars, fpc=fpc.srs)

mysvylm <- svyglm(mass ~ height + sex, starwars.design)
summary(mysvylm)

## Using lm
summary(lm(mass ~ height + sex, data=starwars))

```

### Task 4: Create a Logistic Regression Model to predict if mass exceeds 100lb.

Run a logistic regression model mass being over 100lbs given height and sex. 

```{r}
## Using the Survey Library

## Remove missing mass

starwars <- starwars %>% filter(!is.na(mass))

## Create a new variable called `mass_over100`. 

starwars <- starwars %>%  mutate(
  mass_over100 = case_when(
    mass > 100 ~ 1, ## 1 = Yes, over 100lbs
    mass <= 100 ~ 0)
)

## Using glm: 


```


Based off the above output/model, what is the predicted probability of a male who is 170cm tall being over 100lbs?

a. 0.057
b. 0.061
c. -2.801



